Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-23 analysis/paper/figures.Rmd
added scatter by local plots

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol, nonlocal = nonlocal_symbol), size = 0.05)
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg))
ggsave(plot = p, filename = file.path("../figures", fnpdf))
```

@@

>>>>

```{r scatter-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == keller_mediator, nonlocal = nonlocal_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg))
ggsave(plot = p, filename = file.path("../figures", fnpdf))
```

```{r, scatter_by_local-2}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + 
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol, nonlocal = nonlocal_symbol), size = 0.1) + 
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") + 
  theme(legend.position = "none") +
  xlab("Pleiotropy LOD") + 
  ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", hot_chr, "_scatter-panel.svg")
fnpdf <- paste0("Chr", hot_chr, "_scatter-panel.pdf")
ggsave(plot = p, filename = file.path("../figures", fnsvg), height = ceiling(nlocal / 2))
ggsave(plot = p, filename = file.path("../figures", fnpdf), height = ceiling(nlocal / 2))
```

@@

```{r, ref.label = "scatter_by_local-2"}
```

### 2019-07-23 analysis/paper/paper.Rnw
updated figures
added scatter by local plots

<<>>=
include_graphics("../figures/Chr2_scatter.pdf")
@

>>>>

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 2 hotspot.">>=
include_graphics("../figures/Chr2_scatter.pdf")
@

<<fig.cap = "Chr 2 hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.">>=
include_graphics("../figures/Chr2_scatter-panel.pdf")
@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 5 hotspot.">>=
include_graphics("../figures/Chr5_scatter.pdf")
@

<<fig.cap = "Chr 5 hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.">>=
include_graphics("../figures/Chr5_scatter-panel.pdf")
@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 7 hotspot.">>=
include_graphics("../figures/Chr7_scatter.pdf")
@

<<fig.cap = "Chr 7 hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.">>=
include_graphics("../figures/Chr7_scatter-panel.pdf")
@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 11 hotspot.">>=
include_graphics("../figures/Chr11_scatter.pdf")
@

<<fig.cap = "Chr 11 hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.">>=
include_graphics("../figures/Chr11_scatter-panel.pdf")
@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 13 hotspot.">>=
include_graphics("../figures/Chr13_scatter.pdf")
@

<<fig.cap = "Chr 13 hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.">>=
include_graphics("../figures/Chr13_scatter-panel.pdf")
@
